---
title: "hw3"
author: "Yu Si"
date: "10/20/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(p8105.datasets)

knitr::opts_chunk$set(
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1


```{r}
data("instacart")
instacart = as_tibble(instacart)
```

In this dataset, there are `r nrow(instacart)` rows and `r ncol(instacart)` columns. Variable represents users, order, product and related information. Each row represent each product from order. order-related variable included number, day and hour, such as order_number and days_since_prior_order. product-related variable included product name, aisle and department, such as fresh fruit, Banana, dairy eggs. 

### 1.a

```{r}
instacart %>% 
  count(aisle, sort = TRUE)
```
There are 134 aisles and the most item is fresh vegetable.







