---
title: "hw3"
author: "Yu Si"
date: "10/20/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(p8105.datasets)

knitr::opts_chunk$set(
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1


```{r}
data("instacart")
instacart = as_tibble(instacart)
```

In this dataset, there are `r nrow(instacart)` rows and `r ncol(instacart)` columns. Variable represents users, order, product and related information. Each row represent each product from order. order-related variable included number, day and hour, such as order_number and days_since_prior_order. product-related variable included product name, aisle and department, such as fresh fruit, Banana, dairy eggs. 

### 1.a

```{r}
instacart %>% 
  count(aisle, sort = TRUE)
```
There are 134 aisles and the most item is fresh vegetable.

### 1.b 
```{r }
instacart %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(aisle = reorder(aisle, n)) %>% 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() + 
  labs(title = "the number of items ordered in each aisle") +
  theme(axis.text.x = element_text(angle = 70, hjust = 1))
```


### 1.c
```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4) %>% 
  arrange(desc(n)) %>%
  knitr::kable()

```

### 1.d
```{r}
instacart %>% 
  filter(product_name == c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  ) %>%
  knitr::kable()
```




## Problem 2
```{r}
data("brfss_smart2010")
brfss = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health", response %in% c("Excellent", "Very good", "Good", "Fair", "Poor")) %>% 
  mutate(
    response = factor(response),
    response = fct_relevel(response, "Poor", "Fair", "Good", "Very good", "Excellent"))
  
```


### 2.a
```{r}
brfss %>% 
  filter(year %in% c("2002", "2010")) %>% 
  group_by(year) %>% 
  count(locationabbr) %>%  
  filter(n>=7) %>% 
  knitr::kable()

```


### 2.b
```{r}
brfss %>% 
  group_by(year, locationabbr) %>% 
  filter(response == "Excellent") %>% 
  select(year, locationabbr, data_value) %>% 
  summarize(mean_data_value = mean(data_value, na.rm = TRUE)) %>% 
  ggplot(aes(x= year, y = mean_data_value, color = locationabbr))+
  geom_line(aes(group = locationabbr))

```

### 2.c
```{r}
plot_2006 = 
  brfss %>% 
  group_by(response) %>% 
  filter(year == 2006, locationabbr=="NY") %>% 
  select(locationabbr, response, data_value) %>% 
  ggplot(aes(x = data_value, fill = response)) +
  geom_density(alpha = .4) + theme(legend.position = "none") +
  labs(title = "2006")


plot_2010 = 
  brfss %>% 
  group_by(response) %>% 
  filter(year == 2010, locationabbr=="NY") %>% 
  select(locationabbr, response, data_value) %>% 
  ggplot(aes(x = data_value, fill = response)) +
  geom_density(alpha = .4) + theme(legend.position = "right") + labs(title = "2010")

plot_2006/plot_2010


```




